---
title: "Stacking_CODE"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_width: 14
    fig_height: 10
    fig.align : 'center'
    toc: yes
    number_sections : yes
    code_folding: show
    keep_md: true
---

<hr>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)
```

<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
</style>


# Load package
```{r}
rm(list=ls())

#load packages
library(knitr)
library(tidyverse)
library(magrittr)
library(tidymodels)
library(stacks)
#remotes::install_github("tidymodels/stacks", ref = "main")

options(scipen=999) # turn-off scientific notation like 1e+48
options(tibble.width = Inf)
```

<hr>

<div style="margin-bottom:60px;">
</div>

# Import Data 
```{r}
train <- read_csv("train_wj.csv") %>% mutate(Dayofweek = as.character(Dayofweek))
test <- read_csv("test_wj.csv") %>% mutate(Dayofweek = as.character(Dayofweek))

submission <- read_csv("data/sample_submission.csv")
```

<hr>

<div style="margin-bottom:60px;">
</div>

# Stacking

## N_lunch

### Training and Test Sets
```{r}
# Initial Train-Test Split – rsample
set.seed(2021)
train_split <- initial_split(train, prop = 0.80, breaks = N_lunch)

training_set <- train_split %>% training()
testing_set <- train_split %>% testing()

k_folds_data <- vfold_cv(training_set, v = 5)
```

### Define Pre-processing
```{r}
pca_rec <- recipe(N_lunch ~ ., data = training_set) %>% 
  step_rm(Date, Breakfast, Lunch, Dinner, N_dinner, Rate_lunch, Rate_dinner, Lunch_score, Dinner_score) %>% 
  step_nzv(all_predictors()) %>% 
  step_corr(all_numeric(), -all_outcomes()) %>% 
  step_lincomb(all_numeric(), -all_outcomes()) %>% 
  step_other(all_nominal()) %>% 
  step_normalize(all_numeric(), -all_outcomes()) %>% 
  step_dummy(all_nominal()) %>% 
  step_pca(all_predictors(), num_comp = 5)
  
spline_rec <- recipe(N_lunch ~ ., data = training_set) %>% 
  step_rm(Date, Breakfast, Lunch, Dinner, N_dinner, Rate_lunch, Rate_dinner, Lunch_score, Dinner_score) %>% 
  step_nzv(all_predictors()) %>% 
  step_corr(all_numeric(), -all_outcomes()) %>% 
  step_lincomb(all_numeric(), -all_outcomes()) %>% 
  step_rm(all_nominal()) %>% 
  step_bs(all_predictors()) %>% 
  step_YeoJohnson(all_predictors())

knn_rec <- recipe(N_lunch ~ ., data = training_set) %>% 
  step_rm(Date, Breakfast, Lunch, Dinner, N_dinner, Rate_lunch, Rate_dinner, Lunch_score, Dinner_score) %>% 
  step_nzv(all_predictors()) %>% 
  step_corr(all_numeric(), -all_outcomes()) %>% 
  step_lincomb(all_numeric(), -all_outcomes()) %>% 
  step_normalize(all_numeric(), -all_outcomes()) %>% 
  step_scale(all_numeric(), -all_outcomes())

tidy_rec <- recipe(N_lunch ~ ., data = training_set) %>% 
  step_rm(Date, Breakfast, Lunch, Dinner, N_dinner, Rate_lunch, Rate_dinner, Lunch_score, Dinner_score) %>% 
  step_corr(all_numeric(), -all_outcomes()) %>% 
  step_lincomb(all_numeric(), -all_outcomes()) %>% 
  step_normalize(all_numeric(), -all_outcomes()) %>% 
  step_string2factor(all_nominal()) %>% 
  step_dummy(all_nominal())
```

### Define Models
```{r}
pca_regression_model <- linear_reg() %>% 
  set_mode("regression") %>% 
  set_engine("lm")

spline_model <- linear_reg() %>% 
  set_mode("regression") %>% 
  set_engine("lm")

knn_model <- nearest_neighbor(neighbors = tune()) %>% 
  set_mode("regression") %>% 
  set_engine("kknn")

randomForest_model <- rand_forest(min_n = tune(), trees = tune()) %>% 
  set_mode("regression") %>% 
  set_engine("randomForest")

xgboost_model <- boost_tree(learn_rate = tune(), trees = tune(), tree_depth = tune()) %>% 
  set_mode("regression") %>% 
  set_engine("xgboost")
```

### Define Tuning Control
```{r}
model_control <- control_grid(save_pred = TRUE, save_workflow = TRUE)
model_metrics <- metric_set(mae)
```

### Define Grids
```{r}
knn_grid <- grid_regular(parameters(knn_model), levels = 7)
  
randforest_grid <- grid_regular(parameters(randomForest_model), levels = 3, filter = c(trees > 1))

xgboost_grid <- grid_regular(parameters(xgboost_model), levels = 3, filter = c(trees > 1))
```

### Define Workflows
```{r}
pca_wf <- workflow() %>% 
  add_model(pca_regression_model) %>% 
  add_recipe(pca_rec)

spline_wf <- workflow() %>% 
  add_model(spline_model) %>% 
  add_recipe(spline_rec)

knn_wf <- workflow() %>% 
  add_model(knn_model) %>% 
  add_recipe(knn_rec)
  
randomForest_wf <- workflow() %>% 
  add_model(randomForest_model) %>% 
  add_recipe(tidy_rec)

xgboost_wf <- workflow() %>% 
  add_model(xgboost_model) %>% 
  add_recipe(tidy_rec)
```

### Fit models
```{r}
all_cores <- parallel::detectCores(logical = FALSE)
library(doParallel)
cl <- makePSOCKcluster(all_cores)
registerDoParallel(cl)

pca_res <- fit_resamples(
  pca_wf,
  resamples = k_folds_data,
  control = model_control,
  metrics = model_metrics,
)

spline_res <- fit_resamples(
  spline_wf,
  resamples = k_folds_data,
  metrics = model_metrics,
  control = model_control
)

knn_res <- tune_grid(
  knn_wf,
  resamples = k_folds_data,
  grid = knn_grid,
  metrics = model_metrics,
  control = model_control
)

randomForest_res <- tune_grid(
  randomForest_wf,
  resamples = k_folds_data,
  grid = randforest_grid,
  metrics = model_metrics,
  control = model_control
)

xgboost_res <- tune_grid(
  xgboost_wf,
  resamples = k_folds_data,
  grid = xgboost_grid,
  metrics = model_metrics,
  control = model_control
)
```

```{r}
load("stack.Rdata")
```

### Create Stacks Model
```{r}
ames_stack <- stacks() %>% 
  add_candidates(pca_res) %>% 
  add_candidates(spline_res) %>%
  # add_candidates(knn_res) %>% 
  add_candidates(randomForest_res) %>%
  add_candidates(xgboost_res)

ames_stack <- ames_stack %>% 
  blend_predictions() %>% 
  fit_members()
```

### Self stacking

#### Finalize parameters 
```{r}
knn_final_param <- knn_res %>% show_best("mae") %>% 
  slice(1) %>% 
  select(neighbors)

randomForest_final_param <- randomForest_res %>% show_best("mae") %>% 
  slice(1) %>% 
  select(trees, min_n)

xgboost_final_param <- xgboost_res %>% 
  show_best("mae") %>% 
  slice(1) %>% 
  select(trees:learn_rate)
```

#### Collect model predictions to stack
```{r}
xgboost_stack <- xgboost_res %>% 
  collect_predictions() %>% 
  inner_join(xgboost_final_param) %>% 
  select(id, .row, N_lunch, xgboost = .pred)

randomForest_stack <- randomForest_res %>% 
  collect_predictions() %>% 
  inner_join(randomForest_final_param) %>% 
  select(id, .row, randomforest = .pred)

knn_stack <- knn_res %>% 
  collect_predictions() %>% 
  inner_join(knn_final_param) %>% 
  select(id, .row, knn = .pred)

pca_stack <- pca_res %>% 
  collect_predictions() %>% 
  select(id, .row, pca = .pred)

spline_stack <- spline_res %>%
  collect_predictions() %>% 
  select(id, .row, spline = .pred)
```

#### Create ensemble data
```{r}
stack_df <- xgboost_stack %>% 
  left_join(randomForest_stack) %>% 
  left_join(knn_stack) %>% 
  left_join(pca_stack) %>% 
  left_join(spline_stack) %>% 
  select(-id, -.row)

stack_model <- linear_reg(penalty = .5, mixture = 1) %>% 
  set_mode("regression") %>% 
  set_engine("glmnet") %>% 
  fit(N_lunch~., data = stack_df)

stack_model %>% tidy()
```

#### Finalize submodels
```{r}
xgboost_wf <- xgboost_wf %>% 
  finalize_workflow(xgboost_final_param) %>% 
  last_fit(train_split)

randomForest_wf <- randomForest_wf %>% 
  finalize_workflow(randomForest_final_param) %>% 
  last_fit(train_split)

knn_wf <- knn_wf %>% 
  finalize_workflow(knn_final_param) %>% 
  last_fit(train_split)

pca_wf <- pca_wf %>% last_fit(train_split)

spline_wf <- spline_wf %>% last_fit(train_split)
```

#### Extract Predictions from Submodels
```{r}
stack_final_df <- tibble("model" = list(xgboost_wf, randomForest_wf, knn_wf, pca_wf, spline_wf),
                         "model_names" = c("xgboost", "randomforest", "knn", "pca", "spline")) %>% 
  mutate(pred = map(model, collect_predictions))


stack_final_df <- stack_final_df %>% 
  select(model_names, pred) %>% 
  unnest(pred) %>% 
  select(-.config) %>% 
  pivot_wider(names_from = model_names, values_from = .pred) %>% 
  select(-id, -.row) 
  
predict(stack_model, stack_final_df) %>% 
  bind_cols(stack_final_df) %>% 
  rename("stack" = .pred) %>% 
  pivot_longer(-N_lunch) %>% 
  group_by(name) %>% 
  model_metrics(truth = N_lunch, estimate = value) %>% 
  ungroup() %>% 
  pivot_wider(names_from = .metric, values_from = .estimate) %>% 
  arrange(mae)
```

```{r}
# predict(ames_stack, testing_set) %>% 
#   bind_cols(testing_set %>% select(N_lunch)) %>% 
#   model_metrics(truth = N_lunch, estimate = .pred) %>% 
#   pivot_wider(names_from = .metric, values_from = .estimate)
```

